---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


This is a toy package created as a homework assignment using Jenny's [foofactors] as a template. It is not meant to be actually useful. Scroll below to see my two additions to Jenny's existing functions. 


[foofactors]: https://github.com/jennybc/foofactors


### foofactors

Factors are a very useful type of variable in R, but they can also drive you nuts. This package provides some helper functions for the care and feeding of factors.

### Installation

```{r installation, eval = FALSE}
devtools::install_github("jennybc/foofactors")
```
  
### Quick demo of Jenny's functions

Binding two factors via `fbind()`:

```{r}
library(foofactors)
a <- factor(c("character", "hits", "your", "eyeballs"))
b <- factor(c("but", "integer", "where it", "counts"))
```

Simply catenating two factors leads to a result that most don't expect.

```{r}
c(a, b)
```

The `fbind()` function glues two factors together and returns factor.

```{r}
fbind(a, b)
```

Often we want a table of frequencies for the levels of a factor. The base `table()` function returns an object of class `table`, which can be inconvenient for downstream work. Processing with `as.data.frame()` can be helpful but it's a bit clunky.

```{r}
set.seed(1234)
x <- factor(sample(letters[1:5], size = 100, replace = TRUE))
table(x)
as.data.frame(table(x))
```

The `freq_out()` function returns a frequency table as a well-named `tbl_df`:

```{r}
freq_out(x)
```


### Demo of my functions

* The `is_char()` function detects factors that should be character because the number of unique values equals its length. 


Example: 
```{r}
# Factor that should be a charactor
d <- factor(c('Black', 'Green', 'White')) 

# Not a charactor
e <- factor(c('Black', 'Green', 'Green'))
```

The function returns TRUE or FALSE:
```{r}
is_char(d)
is_char(e)

```


* The function `in_desc()` reorders factors in descending order.


Example:
```{r}
f <- factor(c('Alex', 'Bear', 'Cody'))
```


Function reorders:
```{r}
levels(in_desc(f))
```

